Alex's Notes and Text Fragments for the JOSS Manuscript

### 2021-05-02 paper/paper.Rmd
update methods table

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

```{r setup, echo=FALSE, purl=FALSE}
# important for correct figure placement
# see https://stackoverflow.com/a/49395389/4185785
knitr::knit_hooks$set(plot = function(x, options) {
  knitr::hook_plot_tex(x, options)
})
# knitr::opts_chunk$set(cache = FALSE)
```

```{r setup-2, echo=FALSE, purl=T}
# for knitr spint later
knitr::opts_chunk$set(fig.path = "./paper/figs/",
  cache = F,
  cache.lazy = TRUE)
```

@@

\begin{table}[h]
  \centering
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). }
  \begingroup
  <!-- \begin{adjustbox}{angle=270} -->
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Literature \\
      \toprule
      \multirow{3}{*}{Spatial}        & Spatial Buffering           & \pkg{blockCV}, \pkg{sperrorest}    & "spcv\_buffer", "spcv\_disc()", "spcv\_loo()" & Lit1       \\
                                      & Spatial Blocking            & \pkg{blockCV}, \pkg{sperrorest}  & "spcv\_block",
                                      "spcv\_tiles()"  & Lit1       \\
                                      & Spatial Clustering          & \pkg{sperrorest} & "spcv\_coords" & Lit1       \\
       & Leave-Location-Out & \pkg{CAST}, \pkg{sperrorest}       & "sptcv\_cstf('space\_var')", "spcv\_factor"  & Lit1       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       & "sptcv\_cstf"  & Lit1       \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    & "sptcv\_cluto" & Lit1       \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    & "spcv\_env"    & Lit1       \\
    \end{tabular}
  <!-- \end{adjustbox} -->
  \endgroup\label{tab:sptcv-methods}
\end{table}

>>>>

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
  \newcommand{\specialcell}[2][l]{%
    \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

```{r setup, echo=FALSE, purl=FALSE}
# important for correct figure placement
# see https://stackoverflow.com/a/49395389/4185785
knitr::knit_hooks$set(plot = function(x, options) {
  knitr::hook_plot_tex(x, options)
})
```

```{r setup-2, echo=FALSE, purl=T}
# for knitr spint later
knitr::opts_chunk$set(fig.path = "./paper/figs/",
  cache = T,
  cache.lazy = TRUE)
```

@@

\begin{table}[h]
  \centering
  \footnotesize
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). }
  \begingroup
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Literature \\
      \toprule
      \multirow{6}{*}{Spatial}        & Spatial Buffering           & \specialcell{\pkg{blockCV} \\ \pkg{sperrorest}}    & \specialcell{ \texttt{"spcv\_buffer"} \\  \texttt{"spcv\_disc"}}  & Lit1       \\
      \cmidrule{2-5}
                                      & Spatial Blocking            & \specialcell{\pkg{blockCV} \\ \pkg{sperrorest}}  & \specialcell{  \texttt{"spcv\_block"} \\  \texttt{"spcv\_tiles"}}
                                        & Lit1       \\
  \cmidrule{2-5}
                                      & Spatial Clustering          & \pkg{sperrorest} & \texttt{"spcv\_coords"} & Lit1       \\
                                      \cmidrule{2-5}
       & Leave-Location-Out & \specialcell{\pkg{CAST} \\ \pkg{mlr3}}       & \specialcell{ \texttt{"sptcv\_cstf('space\_var')"} \\ \texttt{"FIXME"}},  & Lit1       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       &  \texttt{"sptcv\_cstf"}  & Lit1       \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    &  \texttt{"sptcv\_cluto"} & Lit1       \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    &  \texttt{"spcv\_env"}    & Lit1       \\
    \end{tabular}
  \endgroup\label{tab:sptcv-methods}
\end{table}
